Supporting Information : Effect of copula on extinction risk

### 2019-02-26 SuppMat.Rmd
age structure results plot upto 25 years

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5,panel.first=grid())
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf
xR<-nlas_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5,panel.first=grid())
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

>>>>

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf[1:26,]
xR<-las_exR$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5,panel.first=grid())
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf[1:26,]
xR<-nlas_exR$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5,panel.first=grid())
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```
